Initial Analysis

### 2019-08-30 Initial_Analysis.Rmd
Modified Neighbour list to be used on other shapefiles. Created an RFMO sub-routine

@@

  # Merge them with SAU data
  suppressWarnings(
    # warning for characters in name, no problem
  DBEM_Neighbors_Data <- Result_table %>% 
     left_join(EEZIDs_List, 
              by = "Name") %>% # Asign EEZ id to each country
    left_join(EEZ_CellID, 
              by = "EEZID") %>% # Asign EEZ id to each country
    left_join(Coor,
              by = "INDEX") %>%  # Inclu
    rename(Country_Territory = Name)

@@

@@

## Sub Routine

```{r Neighbords_Control_Pannel, eval = F, echo = F}

@@

subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru","Brazil"))
#### Grid cell information ####

# List of DBEM INDEX within the EEZ 
#Data provided by Vicki Lam

EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  Neighbor_List <- EstNeighbors(World_EEZs)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

@@

### Function `GetSppDist`

@@

### RFMO analysis

>>>>

EstNeighbors <- function(Shapefile, Partial = "NA"){

@@

  if(Partial == T){
    # If only partial analysis just returns neighbor list
    return(Result_table)

  }else{
  # Merge them with SAU data
  suppressWarnings(
    # warning for characters in name, no problem
  DBEM_Neighbors_Data <- Result_table %>% 
     left_join(EEZIDs_List, 
              by = "Name") %>% # Asign EEZ id to each country
    left_join(EEZ_CellID, 
              by = "EEZID") %>% # Asign EEZ id to each country
    left_join(Coor,
              by = "INDEX") %>%  # Inclu
    rename(Country_Territory = Name)

@@

  } # end ifelse
} # end function

# subset <- World_EEZs %>% filter(Name %in% c("Chile","Peru"))
# EstNeighbors(subset)
# EstNeighbors(subset,T)

@@

### Sub Routine

#### EEZ

```{r EEZ_Neighbords_Control_Pannel, eval = F, echo = F}

@@

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  Neighbor_List <- EstNeighbors(World_EEZs, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

@@

#### RFMOs

```{r RFMO_Neighbords_Control_Pannel, eval = F, echo = F}

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO/",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Name = RFMO_nm_s)

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  RFMO_Neighbor_List <- EstNeighbors(RFMOs_sf, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

write.csv(RFMO_Neighbor_List,
          paste(Data_Path,"Spatial_Data/RFMO_Neighbor_List.csv", sep =""),
          row.names = F)

```
### Function `GetSppDist`

@@
